Energy stable discontinuous Galerkin formulations using discrete differential operators

### 2017-05-23 docs/splitform/main.tex
updating IGA

Writing this in non-conservative form raises the question of local conservation.  Integrating the original equation over $D^k$ and using Gauss' theorem gives
\[
\int_{D^k}\pd{u}{t} + \int_{\partial D^k} \beta_n u = 0.
\]
Taking $v = 1$ on $D^k$ yields
\[
\int_{D^k}\pd{u}{t} + \frac{1}{2}\LRp{\Grad_h\cdot \Pi_N \LRp{ \bm{\beta}u},\bbm{1}_{D^k}} + \frac{1}{2}\LRp{\bm{\beta}\cdot\Grad_h u,\bbm{1}_{D^k}} + \frac{1}{2}\LRp{\LRp{\Grad\cdot \bm{\beta}} u,\bbm{1}_{D^k}} = 0.
\]
The first term gives
\[
\LRp{\Grad_h\cdot \Pi_N \LRp{ \bm{\beta}u},\bbm{1}_{D^k}} = \int_{\partial D^k} \avg{\Pi_N\LRp{\bm{\beta}u}}\cdot\bm{n}.
\]
The second term gives
\[
\LRp{\bm{\beta}\cdot\Grad_h u,\bbm{1}_{D^k}} = \LRp{\Grad u,\bm{\beta}}_{D^k} + \frac{1}{2}\LRa{\jump{u},\bm{\beta}\cdot\bm{n}} = \LRp{u,-\Grad \cdot \bm{\beta}}_{D^k} + \LRa{\avg{u},\bm{\beta}\cdot\bm{n}}
\]
through integration by parts and an assumption that $\bm{\beta}\cdot \bm{n}$ is periodic.  Cancelling volume terms, we end up with the statement of local conservation 
\[
\int_{D^k} \pd{u}{t}  + \frac{1}{2}\int_{\partial D^k} \LRp{\avg{\Pi_N\LRp{\bm{\beta}u}} + \LRp{\Pi_N\LRp{\bm{\beta}}\avg{u}}}\cdot\bm{n} = 0
\]
which is a discrete version of the continuous statement of local conservation.

@@

@@

>>>>

Writing this in non-conservative form raises the question of local conservation.  Integrating the original equation over $D^k$ and using Gauss' theorem gives
\[
\int_{D^k}\pd{u}{t} + \int_{\partial D^k} \beta_n u = 0.
\]
Taking $v = 1$ on $D^k$ yields
\[
\int_{D^k}\pd{u}{t} + \frac{1}{2}\LRp{\Grad_h\cdot \Pi_N \LRp{ \bm{\beta}u},\bbm{1}_{D^k}} + \frac{1}{2}\LRp{\bm{\beta}\cdot\Grad_h u,\bbm{1}_{D^k}} + \frac{1}{2}\LRp{\LRp{\Grad\cdot \bm{\beta}} u,\bbm{1}_{D^k}} = 0.
\]
The first term gives
\[
\LRp{\Grad_h\cdot \Pi_N \LRp{ \bm{\beta}u},\bbm{1}_{D^k}} = \int_{\partial D^k} \avg{\Pi_N\LRp{\bm{\beta}u}}\cdot\bm{n}.
\]
The second term gives
\[
\LRp{\bm{\beta}\cdot\Grad_h u,\bbm{1}_{D^k}} = \LRp{\Grad u,\bm{\beta}}_{D^k} + \frac{1}{2}\LRa{\jump{u},\bm{\beta}\cdot\bm{n}} = \LRp{u,-\Grad \cdot \bm{\beta}}_{D^k} + \LRa{\avg{u},\bm{\beta}\cdot\bm{n}}
\]
through integration by parts and an assumption that $\bm{\beta}\cdot \bm{n}$ is periodic.  Cancelling volume terms involving $\Grad\cdot \beta$, we end up with the statement of local conservation 
\[
\int_{D^k} \pd{u}{t}  + \frac{1}{2}\int_{\partial D^k} \LRp{\avg{\Pi_N\LRp{\bm{\beta}u}} + \LRp{\Pi_N\LRp{\bm{\beta}}\avg{u}}}\cdot\bm{n} = 0
\]
which is a discrete version of the continuous statement of local conservation.

@@

\subsection{Specific discrete cases}

Spectral element methods and mass-lumpable tets: $\Pi_N = I_N$, and the lift operator is just the $\bm{B}$ boundary operator, which you can commute terms such that the scaling of the lift is the same as the lift of the scaling.

CPR GL nodes: conservation for Burgers', but is this just because of the special nature of the flux function cancelling out other terms?  Skew-symmetric variable advection doesn't seem to be conservative.

@@

\section{Numerical experiments}

\begin{itemize}
\item Check ``true'' conservation of discrete DG differentiation formulations - does it converge at $h^{N+2}$ or greater?
\item Copy Ranocha's experiments.  
\item Convergence of 2D advection and (pre-shock) Burgers equation on curvilinear grids: conservative and Lax-Friedrichs fluxes.  
\item Stability (energy/entropy evolution) of 2D advection and Burgers equation on curvilinear grids: conservative and Lax-Friedrichs fluxes.  
\end{itemize}
